\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\setlength{\footskip}{5pt}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-1pt}}
  }
}

\newcommand{\resumeItemComma}[2]{
  \item\small{
    \textbf{#1}{, #2 \vspace{-1pt}}
  }
}

\newcommand{\resumeItemNoTitle}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeItemDate}[3]{
  \item\small{
    \textbf{#1}{ #2 \vspace{-1pt}} \hfill \textit{\small #3}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{10pt}
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-1pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-2pt}}
\newcommand{\resumeSubItemComma}[2]{\resumeItemComma{#1}{#2}\vspace{-2pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2pt}}

%-------------------------------------------
%%%%%%%%%%  RESUME STARTS HERE  %%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://naveen-u.github.io}{\Large Naveen Unnikrishnan}} & Email: \href{mailto:naveenu@umich.edu}{naveenu@umich.edu}\\
  \href{https://naveen-u.github.io}{https://naveen-u.github.io} & Mobile: +91-98470-99907\\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
\vspace{-10pt}
\resumeSubheading
{University of Michigan}{Ann Arbor, MI}
{MSE in Computer Science \& Engineering}{Aug. 2024 -- May 2026 (expected)}
\vspace{1pt}
\resumeSubheading
{Birla Institute of Technology and Science (BITS Pilani)}{Pilani, India}
{BE in Computer Science;  GPA: 8.88/10}{Aug. 2016 -- July. 2020}


%-----------EXPERIENCE-----------------
\section{Experience}
\vspace{-10pt}
\resumeSubheading
{Arcesium}{Bengaluru, India}
{Senior Software Engineer}{July 2020 - June 2024}
\resumeItemListStart
\resumeItemNoTitle{Led development of the integration between Arcesium's data platform, Aquata, and StatPro, a third-party portfolio analytics provider. Collaborated with product and infrastructure teams, created the high-level architecture, led the implementation of the project, and wrote and reviewed code using Python, Apache Spark, Polars, PostgreSQL, Kotlin, and Spring Boot.}
\resumeItemNoTitle{Spearheaded the migration of a key monolithic application hosted on on-premises servers to AWS EKS improving scalability and reducing dev-ops effort by 15\%.}
\resumeItemNoTitle{Full-stack developer – Created multiple key modules, and wrote and reviewed code for Arcesium's invoice processing and cash analysis systems using with Kotlin, Java, Spring, MyBatis, TypeScript, and React.}
\resumeItemListEnd

\resumeSubheading
{Amazon}{Bengaluru, India}
{Software Engineering Intern}{Jan 2020 - June 2020}
\resumeItemListStart
\resumeItemNoTitle{Refactored and unified competitor monitoring configuration pipelines that help improve Amazon's price perception, making them easier to use for internal operations teams, and improving throughput by 20\%.}
\resumeItemListEnd

\resumeSubheading
{Arcesium}{Hyderabad, India}
{Software Engineering Intern}{June 2019 - July 2019}
\resumeItemListStart
\resumeItemNoTitle{Developed a feature to enable users to run custom python code in a secure sandboxed environment to inject custom logic into Arcesium's data-parsing pipelines.}
\resumeItemListEnd

\resumeSubheading
{Identy Touchless ID}{Bengaluru, India}
{Software Engineering Intern - Machine Learning}{June 2018 - July 2018}
\resumeItemListStart
\resumeItemNoTitle{Created CNNs for hand detection and classification using Python and Keras.}
\resumeItemListEnd


%-----------PROJECTS-----------------
\section{Projects}
\resumeItemListStart
\resumeItem{\href{https://github.com/naveen-u/lets-play}{Multiplayer real-time game and chat room}}
{Multiplayer web-based game with chat using Python, Flask, socket-io, Typescript, and React.}
\resumeItem{\href{https://github.com/naveen-u/WingBot}{Discord bot to play interactive games}}
{Discord bot for playing \textit{Anagrams}, \textit{Who's That Pokemon?} and more.}
\resumeItem{\href{https://github.com/naveen-u/nabg}{nabg}}
{\href{https://pypi.org/project/nabg/}{A Python package} to generate sentences from a customizable vocabulary of phrases.}
\resumeItemListEnd


%-----------AWARDS-----------------
\section{Awards \& Recognitions}
\resumeItemListStart
\resumeItemDate{Kishore Vaigyanik Protsahan Yojana (KVPY) Scholarship}{by the Govt. of India}{Mar 2015}
\resumeItemDate{National Talent Search Examination (NTSE) Scholarship}{by the Govt. of India}{Feb 2013}
\resumeItemListEnd

%--------TECHNICAL SKILLS------------
\section{Technical Knowledge}
\resumeItemListStart
\resumeItem{Languages}{: Python, Kotlin, Java, Typescript, Javascript, C++, C, SQL}
\resumeItem{Technologies}{: AWS, Spring Boot, React, Apache Spark, Git, Docker, PostgreSQL, MS SQL Server}
\resumeItem{Courses}{: Data Structures \& Algorithms, Database Systems, Object Oriented Programming, Computer Networks, Network Programming, Cryptography}
\resumeItemListEnd

%-------------------------------------------
\end{document}
